Functional vs. Object Oriented Programming: Productivity comparison

### 2015-10-31 article.tex
Future work added

>>>>

\section{Future work}

We have just demonstrated with a quantitative approach that FP paradigm has real benefits that help the developers to increase their productivity when writing code. Then, a question raise spontaneously: why FP languages are so unpopular, accordingly to TIOBE Index (October 2015)\cite{tiobe}, if they have all of these benefits?

We strongly believe that the most important factor that cuts off from the market these languages is the lack of a consistent and agile Graphic User Interface library support. Nowadays, the user interface and the user experience have become an essential requirement for every kind software. Furthermore, many object oriented implementation, in complex software systems, are more verbose than functional programming because of the code concerning the GUI building. It is not a coincidence that Erlang, for example, runs in the backend of Facebook, WhatsApp and many other software systems.

For future work, when also FP languages will have a valuable GUI support, we want to consider complex systems (not only algorithms) and investigate how the new results will differ from the ones presented here. To conclude, as already mentioned in the previous section, in order to have a global view on the topic we want to analyse other meaningful parameters (i.e. documentation, the comments, the development time, the application domain, etc..) and see if FP paradigm keeps on being better than OOP paradigm.
